Design/Cybernetics: Two Sides of One Coin

### 2019-10-31 MSC-ReadingCourse.tex
minor updates
update intro

        			\item<3-> Important figures and institutions: Kenneth Boulding, Margaret Mead, Heinz von Foerster, Gordon Pask, Humberto Maturana, Paul Pangaro, American Society for Cybernetics, International Society for the Systems Sciences

@@

                \framesubtitle{Types of Systems}

@@

        		    \includegraphics[height=0.8\textheight]{resources/systems.PNG}
                \framesubtitle{Systems and Interactions}
        		    \includegraphics[height=0.8\textheight]{resources/interaction.PNG}

@@

                        The system that is in control must have at least as many states as the system to be controlled.

@@

\section*{Appendix}
	\begin{frame}
		\setbeamercovered{transparent}
		\frametitle{Definition(s) of Cybernetics}
		\framesubtitle{Soooo... What is Cybernetics?}
		\begin{itemize}
			\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
			--- Plato (420s-340s B.C.)
			\item<2->``Cybernetique is the art of governing or the science of government.''\\
			--- André-Marie Ampère (1775-1836)
			\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
			Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
		\end{itemize}
		\setbeamercovered{invisible}
	\end{frame}
	\begin{frame}{NOT a Conversation}
        \framesubtitle{Shannon's Model of Transmission}
        \begin{figure}
            \centering\includegraphics[width=0.8\textwidth]{resources/transmission.PNG}
        \end{figure}
        This model does not scaffold novelty, is pure mechanical, and does not support learning.
    \end{frame}
    \begin{frame}{Mental Models}
        \framesubtitle{Shaping and re-Shaping}
            \centering\includegraphics<1>[width=0.75\textwidth]{resources/models6.PNG}
            \centering\includegraphics<2>[height=0.77\textheight]{resources/models7.PNG}
    \end{frame}

\end{document}

>>>>

        			\item<3-> Important figures and institutions: Kenneth Boulding, Margaret Mead, Heinz von Foerster, Gordon Pask, Humberto Maturana, Paul Pangaro, American Society for Cybernetics, International Society for the Systems Sciences, ...

@@

                \framesubtitle{Types of Systems \cite{pangaro_web}}

@@

        		    \includegraphics[height=0.75\textheight]{resources/systems.PNG}

@@

                        In order to maintain its viability, the system that is in control must have at least as many states as the system to be controlled.

@@

\section*{Appendix}
	\begin{frame}
		\setbeamercovered{transparent}
		\frametitle{Definition(s) of Cybernetics}
		\framesubtitle{Soooo... What is Cybernetics?}
		\begin{itemize}
			\item<1->Ship of the State: The Command of a naval vessel is a metaphor for the governance of a city/state.\\
			--- Plato (420s-340s B.C.)
			\item<2->``Cybernetique is the art of governing or the science of government.''\\
			--- André-Marie Ampère (1775-1836)
			\item<3->``Use the word ‘cybernetics’, Norbert, because nobody knows what it means. This will always put you at an advantage in arguments.''\\
			Widely quoted; attributed to Claude Shannon in a letter to Norbert Wiener in the 1940s.
		\end{itemize}
		\setbeamercovered{invisible}
	\end{frame}
	\begin{frame}{What is NOT a Conversation?}
        \framesubtitle{Shannon's Model of Transmission}
        \begin{figure}
            \centering\includegraphics[width=0.8\textwidth]{resources/transmission.PNG}
        \end{figure}
        This model does not scaffold novelty, is pure mechanical, and does not support learning.
    \end{frame}
    \begin{frame}{Mental Models}
        \framesubtitle{Shaping and re-Shaping}
            \centering\includegraphics<1>[width=0.75\textwidth]{resources/models6.PNG}
            \centering\includegraphics<2>[height=0.77\textheight]{resources/models7.PNG}
    \end{frame}
    \begin{frame}{Interaction}
        \framesubtitle{Configurations \cite{pangaro_web}}
		\begin{figure}
		    \centering
		    \includegraphics[height=0.75\textheight]{resources/interaction.PNG}
		\end{figure}
    \end{frame}
\end{document}
